Nested sampling with multiple scalars

### 2015-09-29 Paper/ms.tex
inputenc
alpha --> beta

\usepackage{dsfont}

@@

\begin{eqnarray}
p(\xx; \alpha_1, \alpha_2) &=& \frac{\pi(\xx)\exp\left[\alpha_1S_1(\xx)+\alpha_2S_2(\xx)\right]}
{Z(\alpha_1, \alpha_2)}
\end{eqnarray}

If we were only interested in a single canonical distribution, for example
with $\alpha_1 = 0.3$ and $\alpha_2 = 0.7$, we could estimate its normalising
constant and by running standard Nested Sampling with ``likelihood''
$L(\xx) = \exp\left[0.3S_1(\xx) + 0.7S_2(\xx)\right]$. However, usually we
are interested in a range of values for $\alpha_1$ and $\alpha_2$, and we
want to know the normalisation $Z(\alpha_1, \alpha_2)$, called the
partition function. This work describes
progress towards solving this class of problems while maintaining the benefits
of Nested Sampling, such as the ability to cope with first-order phase
transitions.

@@

We seek an algorithm for computing the partition function
$Z(\alpha_1, \alpha_2)$ for a range of values of the $\alpha$s, from a single
run. To be considered a variant of Nested Sampling, we require the method
to satisfy the following requirements:
\begin{enumerate}
\item The algorithm should begin with $N$ points drawn from the prior $\pi(\xx)$.
\item The algorithm should seek to explore regions where the values of
$S_1(\xx)$ and $S_2(\xx)$ are greater than what would be expected from the
prior.
\item The algorithm should try to move through a sequence of probability
distributions proportional to $\pi$, but restricted to smaller and smaller
domains for which we can approximately measure the enclosed prior mass.
\item The algorithm should be invariant to monotonic transformations of
$S_1$ and $S_2$, i.e. it should only depend on rankings of $S_1$ and $S_2$
values and not the values themselves.
\end{enumerate}

>>>>

\usepackage{dsfont}
\usepackage[utf8]{inputenc}

@@

\begin{eqnarray}
p(\xx; \beta_1, \beta_2) &=& \frac{\pi(\xx)\exp\left[\beta_1S_1(\xx)+\beta_2S_2(\xx)\right]}
{Z(\beta_1, \beta_2)}
\end{eqnarray}

If we were only interested in a single canonical distribution, for example
with $\beta_1 = 0.3$ and $\beta_2 = 0.7$, we could estimate its normalising
constant and by running standard Nested Sampling with ``likelihood''
$L(\xx) = \exp\left[0.3S_1(\xx) + 0.7S_2(\xx)\right]$. However, usually we
are interested in a range of values for $\beta_1$ and $\beta_2$, and we
want to know the normalisation $Z(\beta_1, \beta_2)$, called the
partition function. This work describes
progress towards solving this class of problems while maintaining the benefits
of Nested Sampling, such as the ability to cope with first-order phase
transitions.

@@

We seek an algorithm for computing the partition function
$Z(\beta_1, \beta_2)$ for a range of values of the $\beta$s, from a single
run. To be considered a variant of Nested Sampling, we require the method
to satisfy the following requirements:
\begin{enumerate}
\item The algorithm should begin with $N$ points drawn from the prior $\pi(\xx)$.
\item The algorithm should seek to explore regions where the values of
$S_1(\xx)$ and $S_2(\xx)$ are greater than what would be expected from the
prior.
\item The algorithm should try to move through a sequence of probability
distributions proportional to $\pi$, but restricted to smaller and smaller
domains for which we can approximately measure the enclosed prior mass.
\item The algorithm should be invariant to monotonic transformations of
$S_1$ and $S_2$, i.e. it should only depend on rankings of $S_1$ and $S_2$
values and not the values themselves.
\end{enumerate}

The algorithm works as follows.
